How young children integrate information sources to infer the meaning of words

### 2020-11-26 paper/supplementary_material.Rmd
add AIS analysis files

```{r}
#fig2 <- ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.3,1), common.legend = F)
#ggsave(plot = fig2, "../figures/figureS2.png", width = 12, height = 4)
```

>>>>

```{r}
#fig2 <- ggarrange(plot_aoa, plot_me, cor_plot_me,  labels = c("A","B","C"), nrow = 1, widths = c(1,1.2,1), common.legend = F)
#ggsave(plot = fig2, "../figures/figureS2.png", width = 12, height = 3, scale = 1.5)
```
